INSTALL
=======

* You can start by copying the `amcapaper.tex' to a new file and
  simply replace the appropriated text. 

* Put the `amca.bst' and `amca.cls' in some directory where LaTeX can see it. 
  It may be the same directory where you are writing your paper or a
  directory in the TEXINPUTS path. (In Linux good candidates are
  `/usr/local/tex' and `/usr/local/share/tex'). 
 
REQUIRED LATEX PACKAGES:
=======================

The following LaTeX packages are required by the `amca' class:

   calc, indentfirst, authblk, natbib, babel, color, hyperref,
   nameref, url, times, fontenc

OPTIONS FOR AMCA CLASS:
======================

The AMCA class is derived from the standard LaTeX `article' class, so
that it accepts its options. Additional options are:

* english/spanish/portuguese: choose the language of the article
                              (default: `english'). 

* links/nolinks: activate/deactivate links for equations, references,
                 tables, figures, using the `hyperref' package. We 
		 recommend to activate this option. (default: `links'). 

Example of usage:

    \documentclass[oneside,a4paper,spanish,nolinks]{amca}


AUTHORS AND AFFILIATIONS:
========================

This is managed with the `authblk' package that is already included by
the `amca' class. If in doubt, consult the `authblk.dvi' file that
comes with the package. For most cases, the example provided should be
enough. If all the authors belong to the same affiliation then use a
the macro `\voidaffil' as the affiliation character code, e.g.

   \author[\voidaffil]{First A. Author},  
   \author[\voidaffil]{Second B. Author}
   \author[\voidaffil]{Third C. Author}
   \author[\voidaffil]{Fourth D. Author}
   %
   \affil[\voidaffil]{Grupo de Mec\'anica Computacional, 
   Universidad Nacional de Villa Carolina, 
   Los Alerces 3492, 4200 Villa Carolina, Argentina, 
   gmc@uncarolina.edu.ar, http://www.uncarolina.edu.ar/gmc}

If an author belongs to several affiliations then the corresponding
affiliation character codes should be introduced separated by commas,
e.g.

   \author[a,b]{First A. Author},  

RECOMMENDATIONS FOR HYPHENATION:
================================

The AMCA class includes automatically the `babel' package so that,
LaTeX will hyphenate the article appropriately. However it is a common
mistake that articles written in spanish or portuguese, are hyphenated
according to english hyphenation rules. This is in most cases due to
an incomplete configuration of the LaTeX distribution. Please, check
that the article is correctly hyphenated. 

RECOMMENDATIONS FOR GENERATION OF THE PDF FILES:
================================================

For LaTeX users it is highly recommended to generate the PDF file
directly from the sources using the `pdflatex' program. Most common
`TeX' distributions (as `teTeX') include `pdflatex'. If the PDF is
generated from a PostScript file with `ps2pdf', please be sure
that the quality of the article is not degraded, in that case the
instructions below could be helpful.

LINKS / HYPERREF
================

If you generate the PDF file from Postscript, then you probably will
no get the links. 

If you generate the PDF file from the DVI file, then you must modify
the `amca.cls' package so that the `hyperref' package uses the `dvips'
driver. This is done by changing the call to the `hyperref' package
(at the bottom of the `amca.cls' file) like this

\RequirePackage[dvips,colorlinks,linkcolor=blue,%
                urlcolor=url,citecolor=blue]{hyperref}

PCTeX users should do this modificacation, since PCTeX generates the
PDF via an intermediate DVI file.

PDF generation from PS file
===========================

It is advisable to check if the PDF file produced meets the format
requirements. Open it with an Acrobat Reader.

If the default configuration of your dvips or Ghostscript package is
set to some size other than A4, then you will explicitly have to set
the article size to A4 when running either of the programs `dvips',
`dvipdf' or `ps2pdf'.

For avoiding problems with specific fonts possibly used in your
article please include all fonts when generating the PDF file.

Font specification with LaTeX: 
==============================

In order to obtain a good typographic quality of your PDF document,
ensure that only Type 1 (resolution-independent) vector fonts are used
instead of the Type 3 raster graphics fonts originally used by (you
can check the type of fonts actually used in your PDF document in
Acrobat Reader: File / Document Info / Fonts). Provided that Type 1
vector fonts are included in your LaTeX distribution for both text and
mathematics typesetting (which is the case for many modern LaTeX
distributions), try to run the `dvips' program with the following
options in order to substitute all Type 3 fonts by scalable Postscript
Type 1 fonts:

    $ dvips -Pamz -Pcmz [other options] filename

Afterwards, use your preferred Postscript to PDF converter for
generating the PDF file of your abstract.

Further information concerning PDF file generation with LaTeX can be
found on the web (see
e.g. http://www.tex.ac.uk/tex-archive/info/webguide/webguide.html). For
information and software concerned to LaTeX itself see
e.g. http://www.tex.ac.uk/CTAN/latex/.

BIBTEX
======

The package includes the file `amca.bst', which is used as
bibliographic style inside the class. It is based on Harvard style
referencing (a.k.a. author-year style, e.g. Skywalker and Yoda
2008). 

Examples of use of \cite{} command and friends

  \citet{key} ==>>                Jones et al. (1990)
  \citep{key} ==>>                (Jones et al., 1990)
  \citep[chap. 2]{key} ==>>       (Jones et al., 1990, chap. 2)
  \citep[e.g.][]{key} ==>>        (e.g. Jones et al., 1990)
  \citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., p. 32)
  \citeauthor{key} ==>>           Jones et al.
  \citeyear{key} ==>>             1990

FAQ:
===

1./ What version of teTeX or TexLive is required?

The `amca.cls' package has been tested with teTeX 2.0.2-13 that comes
with the Fedora Core 2 Linux distribution. It should run OK with
subsequent versions of teTeX and TexLive .

2./ Should I indent the first paragraph of each section?

Short answer: Yes, this is already included in the `amca.cls',

Long answer: The `article' class that comes with LaTeX and from which
the `amca.cls' is derived, DOES NOT indent the first paragraph of each
section. Most journals use this style. In the AMCA style the first
paragraph of each section *is* indented and this is done with the
`indentfirst' package.
